I would like to express my gratitude to my advisor, George Wolberg,
for his support, invaluable suggestions and encouragement 
on issues that were beyond my research.
His systematic thinking and many comments and ideas 
have undoubtedly boosted the quality of the work.

I also owe a lot to my co-advisor, Zhigang Zhu who brought me to the computer
vision research area. 
My technical skills and research interest were gradually built when 
working with Professor Zhu during my early stage of the doctorate journey.
My sincere thanks go to the rest of my thesis committee as well, 
Ioannis Stamos who gave insightful suggestions and comments 
on my research and provided the range datasets for the experiments and
Michael Reed who spent time to serve on my thesis committee
as an outside member and to supervise my dissertation defense.

I would like to give a special thank-you to Siavash Zokai.
His solid background knowledge, in-depth discussion and technical supports 
helped me out from those difficult time frequently.
I would also like to thank all those who have contributed to this work 
by providing valuable input and suggestions.
Gene Yu shared experiences on point cloud data processing and highlighting.
Hadi Fadaifard's normal detection code made major facades detection much easier.
Hao Tang suggested some literature and techniques on related work.

I would also like to express gratitude to my parents.
Special thanks to my mother-in-law who took care of little Brian, 
my lovely son, so that I could be more focused on this research.
Finally, I must express my appreciation to my wife, Pingna.
She has been a source of constant support throughout 
the many long days spent working on this dissertation. 
For this, and many other things, I am profoundly grateful.

